Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2019-01-19 SupportingInformation.Rmd
fixed error

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

>>>>

if (!dir.exists(tempo)){
  dir.create(tempo)
}
resloc<-paste(tempo,"/",sep="")
# for gumbel with spearman and kendall method
Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,method="spearman",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model=model)

@@

resloc<-paste(tempo,"/",sep="")
# for gumbel with spearman and kendall method
Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,method="spearman",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model=model)

@@

if (!dir.exists(tempo)){
  dir.create(tempo)
}
resloc<-paste(tempo,"/",sep="")
# for survival gumbel with spearman and kendall method
Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,method="spearman",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model=model)

@@

resloc<-paste(tempo,"/",sep="")
# for survival gumbel with spearman and kendall method
Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,method="spearman",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model=model)

@@

if (!dir.exists(tempo)){
  dir.create(tempo)
}
resloc<-paste(tempo,"/",sep="")
# for joe with kendall method only

@@

resloc<-paste(tempo,"/",sep="")
# for joe with kendall method only

@@

if (!dir.exists(tempo)){
  dir.create(tempo)
}
resloc<-paste(tempo,"/",sep="")
# for survival joe with kendall method only

@@

resloc<-paste(tempo,"/",sep="")
# for survival joe with kendall method only

@@

# for survival clayton with spearman and kendall method
  Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,method="spearman",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=p0,model=model)

@@

# for gumbel with spearman and kendall method
  Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,method="spearman",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=p0,model=model)

@@

# for survival gumbel with spearman and kendall method
  Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,method="spearman",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=p0,model=model)

@@

# for joe with kendall method only

@@

# for survival joe with kendall method only
